Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-05-29 docs/00-manuscripts/ieee/ieee-manuscript.tex
sell RC a bit better

The algorithm implementations of the following packages have been used: xgboost \cite{chen2016} (\textit{Extreme Gradient Boosting}), kernlab \cite{kernlab} (Support Vector Machine) and glmnet \cite{glmnet} (penalized regression).
The filter implementations of the following packages have been used: praznik \cite{praznik}, FSelectorRcpp \cite{fselectorrcpp}.
Package mlr \cite{mlr} was used for all modeling related steps.
drake \cite{drake} was used for structuring the work and reproducibility.
This study is available as a research compendium on Zenodo (\url{10.5281/zenodo.2635403}).
The code base is available on GitHub (\url{https://github.com/pat-s/2019-feature-selection}).

>>>>

The algorithm implementations of the following packages have been used: xgboost \cite{chen2016} (\textit{Extreme Gradient Boosting}), kernlab \cite{kernlab} (Support Vector Machine) and glmnet \cite{glmnet} (penalized regression).
The filter implementations of the following packages have been used: praznik \cite{praznik}, FSelectorRcpp \cite{fselectorrcpp}.
Package mlr \cite{mlr} was used for all modeling related steps.
drake \cite{drake} was used for structuring the work and reproducibility.
This study is available as a research compendium on Zenodo (\url{10.5281/zenodo.2635403}).
Besides the availability of code and manuscript sources, a static webpage is available at (\url{https://github.com/pat-s/2019-feature-selection}),listing more side-analyses that were carried out through the creation of this study.
